Appendix A

### 2024-04-17 manuscript/Appendix A.qmd
edits, refs ect

---
title: Appendix A
subtitle: For the article 'Making use of spatially biased variables in ecosystem condition accounting – a GIS based workflow'
author:
  - name: Anders Lorentzen Kolstad
    email: anders.kolstad@nina.no
    orchid: https://orcid.org/0000-0002-9623-9491
    affiliations: 
        - id: nina
          name: Norwegian Institute for Nature Research
          department: Department of Terrestrial Ecology
          address: Pb 5685 Torgarden
          city: Trondheim
          postal-code: 7485
  - name: Matthew Grainger
    email: matthew.grainger@nina.no
    orchid: https://orcid.org/0000-0001-8426-6495
    affiliations:
        - ref: nina
  - name: Marianne Evju
    email: marianne.evju@nina.no
    orchid: https://orcid.org/0000-0001-7338-5376
    affiliations:
        - id: nina2
          name: Norwegian Institute for Nature Research
          department: NINA Oslo
          address: Sognsveien 68
          city: Oslo
          postal-code: NO-0855
date: last-modified
format:
  pdf
editor: 
  markdown: 
    wrap: sentence
crossref:
  fig-title: |
    Figure S
  tbl-prefix: Fig S.
  fig-prefix: Fig S.
  tbl-title: |
    Table S
execute:
  echo: false
---

@@

{{< pagebreak >}}
```{r tbl-EEA}
#| tbl-cap: "Indicator values for three ecosystem condition indicators in three 
#| Norwegian municipalities. Values are medians with 2.5 and 97.5 percentiles
#| for the distribution of possible values."

(tbl <- readRDS("../output/EEA-tbl.RDS"))
```

>>>>

---
title: Appendix A
subtitle: For the article 'Making use of spatially biased variables in ecosystem condition accounting – a GIS based workflow'
author:
  - name: Anders Lorentzen Kolstad
    email: anders.kolstad@nina.no
    orchid: https://orcid.org/0000-0002-9623-9491
    affiliations: 
        - id: nina
          name: Norwegian Institute for Nature Research
          department: Department of Terrestrial Ecology
          address: Pb 5685 Torgarden
          city: Trondheim
          postal-code: 7485
  - name: Matthew Grainger
    email: matthew.grainger@nina.no
    orchid: https://orcid.org/0000-0001-8426-6495
    affiliations:
        - ref: nina
  - name: Marianne Evju
    email: marianne.evju@nina.no
    orchid: https://orcid.org/0000-0001-7338-5376
    affiliations:
        - id: nina2
          name: Norwegian Institute for Nature Research
          department: NINA Oslo
          address: Sognsveien 68
          city: Oslo
          postal-code: NO-0855
date: last-modified
bibliography: bibliography.bib
format:
  pdf
editor: 
  markdown: 
    wrap: sentence
crossref:
  fig-title: |
    Figure S
  tbl-prefix: Fig S.
  fig-prefix: Fig S.
  tbl-title: |
    Table S
execute:
  echo: false
---

@@

| HIA class | Lower limit | Upper limit |
|-----------|-------------|-------------|
| 0         | 0           | \<1         |
| 1         | 1           | \<6         |
| 2         | 6           | \<12        |
| 3         | 12          | 15.44       |
: Data ranges used to categorise the Norwegian Land Use Intensity Index (the Infrastructure Index) [@erikstad2023] in the new categorical variable Homogeneous Impact Areas (HIA). {#tbl-ranges}

{{< pagebreak >}}

```{r tbl-EEA}
#| tbl-cap: "Indicator values for three ecosystem condition indicators in three 
#| Norwegian municipalities. Values are medians with 2.5 and 97.5 percentiles
#| for the distribution of possible values."

(tbl <- readRDS("../output/EEA-tbl.RDS"))

```

# References {.unnumbered}

::: {#refs}
:::
